---
title: "Module 4"
author: "Albert Christian F. Brigino"
date: "2/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Module 4

Your assignment:
The following data was collected by the local hospital. This data set contains 5 variables based on observation of 8 patients. In addition to the measurements of the patients checking in to the hospital that night, this data provides the patients' histories regarding the frequency of their visits to the hospital in the last 12 months.
This data displays the measurement of blood pressure, first assessment by general doctor (bad=1, good =0) titled "first," the second assessment by external doctor (called "second"), and the last row provides the head of the emergency unit's decision regarding immediate care for the patient based on the values 0 or 1 (low = 0, high =1).
The names of your variables are as follows: "Freq","bloodp","first”, " second”, ”finaldecision”
The rows 
1.    "0.6","103","bad","low","low”
2.     "0.3","87","bad","low","high”
3.     "0.4","32","bad","high","low”
4.      "0.4","42","bad","high","high"
5.     "0.2","59","good","low","low”
6.      "0.6","109","good","low","high”
7.     "0.3","78","good","high","low”
8.      "0.4","205","good","high","high”
9.      "0.9","135",”NA","high","high"
10.    "0.2","176",”bad","high","high”
Here is Clarification hint:
Frequency <- c(0.6,0.3,0.4,......
BP <- c(103,87,32,42,.....
First <- c(1,1,1,.....
Second <- c(0,0,1,1,...
FinalDecision <- c(0,1,0,1,...
Your first assignment: Create a side-by-side boxplot (boxplot(x, ...)) and and histogram ((hist(x, ...)). 
Discuss the outcome of your results regarding patients BPs & MD’s Ratings.
Post your result in your blog and code on GitHub. 

```{r 1}

#Vectors and Data Frame

Freq <- c(0.6, 0.3, 0.5, 0.5, 0.2, 0.5, 0.3, 0.4, 0.9, 0.2)
bloodp <- c(103, 87, 32, 42, 59, 109, 78, 205, 135, 176)
first <- c(1, 1, 1, 1, 0, 0, 0, 0, NA, 1)
second <- c(0, 0, 1, 1, 0, 0, 1, 1, 1, 1)
finaldecision <- c(0, 1, 0, 1, 0, 1, 0, 1, 1, 1)

hspPatients <- data.frame(Freq, bloodp, first, second, finaldecision)
hspPatients

#Frequency Boxplots

boxplot(Freq ~ first, hspPatients,
        main = "Visit Frequency vs. First Results",
        xlab = "First Assessment Results",
        ylab = "Frequency of Visits",
        names = c("good", "bad"))
boxplot(Freq ~ second, hspPatients,
        main = "Visit Frequency vs. Second Results",
        xlab = "Second Assessment Results",
        ylab = "Frequency of Visits",
        names = c("good", "bad"))
boxplot(Freq ~ finaldecision, hspPatients,
        main = "Visit Frequency vs. Immediate Care",
        xlab = "Final Decision Results",
        ylab = "Frequency of Visits",
        names = c("No", "Yes"))

#BP Boxplots

boxplot(bloodp ~ first, hspPatients,
        main = "Blood Pressure vs. First Results",
        xlab = "First Assessment Results",
        ylab = "Frequency of Visits",
        names = c("good", "bad"))
boxplot(bloodp ~ second, hspPatients,
        main = "Blood Pressure vs. Second Results",
        xlab = "Second Assessment Results",
        ylab = "Frequency of Visits",
        names = c("good", "bad"))
boxplot(bloodp ~ finaldecision, hspPatients,
        main = "Blood Pressure vs. Immediate Care",
        xlab = "Final Decision Results",
        ylab = "Frequency of Visits",
        names = c("No", "Yes"))

#Histograms

hist(bloodp,
     main = "Blood Pressure Distribution",
     xlab = "Blood Pressure")
hist(Freq,
     main = "Visit Frequency Distribution",
     xlab = "Visit Frequency")
hist(finaldecision,
     main = "Final Decision Distribution")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
