---
title: "Module 7"
author: "Albert Christian F. Brigino"
date: "2/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Module # 7 assignment


Download any type of data (from the web or use datasets package) or create your own set. 

Then, on the second step, determine if generic function as discussed in this module can be assigned to your data set, and if not, why? (Example, here is list of data set in R)
data("mtcars")
head (mtcars, 6)
list(mtcars, 6)

```{r Arrests}
data("PlantGrowth")
head(PlantGrowth, 6)
list(PlantGrowth, 6)
```
Example of data set for S3

s <- list(name = "Myself", age = 29, GPA = 3.5) 
> s3
$name
[1] "Myself"
$age
[1] 29
$GPA
[1] 3.5
For S4 it is a reminder, S4 objects are created using the new() function. 

> s4 <- new("student",name="Myself", age=29, GPA=3.5)
 > s4
An object of class "student"
Slot "name":
[1] "Myself"
Slot "age":
[1] 29
Slot "GPA":
[1] 3.5


```{r 3&4}
#Creates S3 Class
s3 <- list(weight = 6.9, group = "trt2") 
s3

setClass("Batch 1", slots=list(weight = "numeric", group = "character"))

s4 <- new("Batch 1", weight = 6.9, group = "trt4")
s4

isS4(s3)
isS4(s4)

rbind(PlantGrowth, s3)
rbind(PlantGrowth, s4)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
