---
title: "Module 5"
author: "Albert Christian F. Brigino"
date: "2/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
```

## Assignment

The focus of this assignment is learn about Matrix in R. 
For more detail how to work with Matrix in R, click here  Download herefor the worksheet in Matrix.
Plus a more detail on what is inverse Matrix, click here  Download here.  Download .This reference was created by Engineering Mathematics first aid kit published by Pearson Education.  
The R code for inverse Matrix: solve(A). This code is the Inverse of A where A is a square matrix. For complete list of Matrix Algebra in R, visit  Dr. Kabacoff, Quick-R at https://www.statmethods.net/advstats/matrix.html (Links to an external site.)

Your Assignment:
Find the value of inverse of a matrix, determinant of a matrix by using the following values:
A=matrix(1:100, nrow=10)
B=matrix(1:1000, nrow=10)
Post your result and procedure you took on your blog.
A good start will be:
>A <- matrix(1:100, nrow=10)  
>B <- matrix(1:1000, nrow=10)



```{r Mod5}

#Create starting matrices
A <- matrix(1:100, nrow=10)  
B <- matrix(1:1000, nrow=10)

#Transpose
tA <- t(A)
tB <- t(B)

##Create random samples with corresponding sizes
#a <- c(sample(1:100,100, replace = FALSE))
a <- replicate(10,as.integer(abs(rnorm(10)*10)))
#b <- c(sample(1:1000,1000, replace = FALSE))
b <- replicate(10,as.integer(abs(rnorm(100)*100)))

#Transposed matrices multiplied by corresponding vectors
A2 <- tA*a
B2 <- tB*b

#Conversion of vectors into matrices
a2 <- matrix(a, nrow = 10)
b2 <- matrix(b, nrow = 10)

#Multiplication of matrices
newA <- a2%*%A2
newB <- b2%*%B2

#Determinant and Inverse
det(newA)
solve(newA)
ginv(A)

det(newB)
solve(newB)

#Checking results using MASS
ginv(A)
ginv(B)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
