---
title: "Module 12"
author: "Albert Christian F. Brigino"
date: "4/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## % Armor Reduction

Function designed to calculate % armor reduction (not to be confused with % armor penetration). % armor reduction stacks multiplicatively and will not function below zero. Currently, only two categories affect this stat, champion abilities and a single item (Black Cleaver).  

```{r percentReduction}
pRedCalc <- function (champAbility, BC){
  #Throws error message when below minimum BC stacks
  ifelse(BC < 0, pRed <- "Error: invalid Black Cleaver stacks (try 0-6)",
  #Stand-alone line for if BC stacks are zero and therefore not applicable to overall calculation
  ifelse(BC < 1, ifelse(champAbility >= 0 & champAbility < 1, pRed <- champAbility, "Error: Invalid ability value"),
  #Applies to all valid calculations with BC stacks included
  ifelse(BC < 7, pRed <- 1-(1-champAbility)*(1-(BC*.05)), pRed <- "Error: invalid Black Cleaver stacks (try 0-6)")))
  
  #Checks to see if pRed <= 0, if so, % armor reduction is not calculated
  ifelse(pRed > 0, return(pRed), "Not Applicable")
}
```

## Lethality Armor Penetration

Function designed to calculate applied lethality of a champion based on total lethality gained according to the current level of a champion. As champion level increases, the ratio at which lethality translates to flat armor penetration also increases. 

```{r lethality}
lethCalc <- function(lethality, level){
  faPenLeth <- lethality * (0.6 + 0.4 * level / 18)
  #Does a check to ensure valid lethality and level inputs and returns an error message if invalid
  ifelse(lethality > 0 & level > 0  & level < 19, return(faPenLeth), "Error: Invalid level or lethality")
}
```

## Test Calculations

```{r test}

#Example of valid % reduction calculation
pRedCalc(.24, 6)

#Example of invalid % reduction calculation
pRedCalc(.15, 8)

#Example of valid lethality calculation
lethCalc(36, 18)

#example of invalid lethality calculation
lethCalc(24, 19)
```

